\pdftitle

### 2018-05-23 maxNt_v3.tex
V3

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2018-05-18T15:43:51+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

\usepackage[%final,%
nonatbib]{nips_2017}

\newcommand*{\firstdraft}{4 November 2015}

@@

@@

\subsubsection*{Acknowledgments}

To be added after review.
\iffalse PGLPM thanks Mari \amp\ Miri for continuous encouragement and affection,
Buster Keaton for filling life with awe and inspiration, and the developers
and maintainers of \LaTeX, Emacs, AUC\TeX, MiK\TeX, arXiv, biorXiv,
PhilSci, Hal archives, Python, Inkscape, Sci-Hub for making a free and
unfiltered scientific exchange possible.\fi

>>>>

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2018-05-23T09:12:59+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

\usepackage[preprint,%
nonatbib]{nips_2018}

\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\published}{22 May 2018}

@@

\vspace{-2em}
\begin{center}
  \footnotesize\published
\end{center}
\medskip

@@

\subsubsection*{Acknowledgements}

PGLPM thanks Mari \amp\ Miri for continuous
encouragement and affection; Buster Keaton for filling life with awe and
inspiration; the developers and maintainers of \LaTeX, Emacs, AUC\TeX, Open
Science Framework, Python, Inkscape, Sci-Hub for making a free and
unfiltered scientific exchange possible.
